\documentclass[]{deedy-resume-openfont}

\begin{document}

\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%    TITLE NAME
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\namesection{Oindril}{Dutta}{Developer, Founder and Hackathon Enthusiast\\
\href{mailto:duttaoindril@gmail.com}{duttaoindril@gmail.com} | \href{http://duttaoindril.github.io/}{duttaoindril.github.io} | 408.658.8961 | San Jose, CA}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COLUMN ONE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.32\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\vspace{\topsep}
\subsection{Programming}
\vspace{\topsep}
\descript{Fluent:}
Java \textbullet{} Android \textbullet{} \LaTeX\ \textbullet{} JSON\\
HTML \textbullet{} CSS \textbullet{} JS \textbullet{} JQuery \\
\descript{Proficient:}
Ruby \textbullet{} Rails \textbullet{} PHP \textbullet{} Python \\
AJAX \textbullet{} C++ \textbullet{} MySQL \textbullet{} .Net
\sectionsep

\subsection{Technologies}
\vspace{\topsep}
\descript{Proficient:}
Git \textbullet{} Eclipse \textbullet{} Firebase \\
PhoneGap \textbullet{} Bootstrap \textbullet{} Zurb

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}
\vspace{\topsep}
\subsection{San Jose State University}
\vspace{\topsep}
\descript{BS in Computer Science}
\location{Expected June 2019 | San Jose, CA}
\sectionsep

\subsection{Monta Vista High School}
\vspace{\topsep}
\location{Grad. June 2015 | Cupertino, CA}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     VOLUNTEERING
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Volunteering}
\vspace{\topsep}
\subsection{LinkedIn Job Shadow}
\vspace{\topsep}
Great volunteer Job Shadow event to\\learn about life and work at LinkedIn.
\sectionsep

\subsection{Study Buddy Society}
\vspace{\topsep}
Tutored and helped fellow students\\on subjects like Math, Physics \& CS.
\sectionsep

\subsection{Library Tech Toolbar}
\vspace{\topsep}
I taught library patrons how to get ebooks to facilitate the shift to them.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links}
\vspace{\topsep}
\href{http://duttaoindril.github.io/}{\custombold{duttaoindril.github.io}} \\
\href{http://github.com/duttaoindril}{Github.com/ \custombold{duttaoindril}} \\
\href{https://www.linkedin.com/in/debarghyadas}{LinkedIn.com/in/ \custombold{oindrildutta}} \\
\href{http://www.facebook.com/duttaoindril}{FB.com/ \custombold{duttaoindril}} \\
\href{twitter.com/intent/tweet?screen_name=DuttaOindril}{Twitter.com/ \custombold{duttaoindril}} \\
\href{http://teamtreehouse.com/duttaoindril}{TeamTreehouse.com/ \custombold{duttaoindril}} \\
References available on request.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     INTERESTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Interests}
\vspace{\topsep}
\location{Professional:} Data analysis \textbullet{} App Design \& Dev\\
Web Design \& Dev \textbullet{} Security\\
\location{Personal:} Hackathons \textbullet{} Photography \textbullet{} Reading \\
Ice skating \textbullet{} Archery \textbullet{} Basketball

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LANGUAGES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{languages}
\vspace{\topsep}
English \textbullet{} Bengali \textbullet{} Hindi \textbullet{} Spanish

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COLUMN TWO
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage}
\hfill
\begin{minipage}[t]{0.67\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{Abroadler}
\descript{| Co-Founder; CTO}
\location{July 2015 - Present | San Francisco, CA | \href{http://abroadler.com}{abroadler.com}}
Co-Founder and CTO of a budding startup for students that travel abroad.
\sectionsep

\runsubsection{GuptaChem}
\descript{| Freelance Web Developer}
\location{Jan 2015 – July 2015 | Cupertino, CA | \href{http://guptachem.com}{guptachem.com}}
Developed from scratch a Rails e-commerce site to advertise/sell SAT II Chem classes.
\sectionsep

\runsubsection{Media Elements LLC}
\descript{| Backend and Frontend Web Dev Intern}
\location{July 2014 – Jan 2015 | San Francisco Bay Area, CA | \href{http://www.myownevents.com}{myownevents.com}}
Developed an existing laravel website that's a social network, calendar, \& event tracker.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Awards}
\runsubsection{Myo Messenger}
\descript{| 1\textsuperscript{st} place +  Myo Sponsor prize winner}
\location{August 2014 | Hero Hacks | \href{duttaoindril.github.io/MyoMessenger}{duttaoindril.github.io/MyoMessenger}}
IM app to let the speech-impaired send translated Sign Language gestures using Myo.
\sectionsep

\runsubsection{Trouve}
\descript{| 3\textsuperscript{rd} place prize}
\location{June 2014 | BeyondHacks | \href{trouve.paperplane.io}{trouve.paperplane.io}}
Crowd-sourced location finder app to pin anything and let others find everything.
\sectionsep

\runsubsection{Seekr}
\descript{| Dice Sponsor Prize}
\location{June 2014 | HackSummit | \href{seekr.paperplane.io}{seekr.paperplane.io}}
100,000 searchable jobs displayed on a map, filterable by location, skill, \& user stats.
\sectionsep

\runsubsection{ViewMe}
\descript{| Pubnub Sponsor Prize}
\location{July 2014 | Angel Hacks Sillicon Valley | \href{duttaoindril.github.io/ViewMe} {duttaoindril.github.io/ViewMe}}
Control any 3D object with any pc/phone camera using gestures with your torso.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
\runsubsection{Teen Hackathon}
\descript{| Founder \& CEO}
\location{August 2014 – March 2015 | San Jose, CA | \href{http://teenhackathon.com/}{teenhackathon.com}}
Hosted \& led my hackathon to teach coding \& close the gender/diversity gap in tech.
\sectionsep

\runsubsection{Monta Vista Comp Sci Club}
\descript{| Head of Tech \& Webmaster}
\location{August 2014 – June 2015 | Cupertino, CA | \href{http://www.mvcompsci.com/}{mvcompsci.com}}
Portal for MVCS to publish the latest news and track member attendance at meetings.
\sectionsep

\runsubsection{Slapp}
\descript{| Team Lead \& Myo + Web Developer}
\location{February 2015 | HS Hacks II | \href{http://duttaoindril.github.io/Slapp/}{duttaoindril.github.io/Slapp}}
App for smartwatches/myos/phones to detect slapps \& exchange contact + other info.
\sectionsep

\runsubsection{MixChat}
\descript{| Team Lead \& Web Developer}
\location{December 2014 | Angel Hacks | \href{http://mix.paperplane.io/}{duttaoindril.github.io/MixChat}}
Universal IM app to talk freely between multiple IMs like FB, gmail, kik, skype, etc.
\sectionsep

\runsubsection{HappyShirts}
\descript{| .Net Developer}
\location{August 2014 | Shirts.io | \href{http://happyshirts.paperplane.io/}{happyshirts.paperplane.io}}
Preview a t-shirt on yourself with any pc/phone camera with just an image of the shirt.
\sectionsep

\runsubsection{StayUp}
\descript{| Team Lead \& Android Developer}
\location{June 2014 | AT\&T Mobile App Hacks | \href{http://duttaoindril.github.io/UPITTY}{duttaoindril.github.io/UPITTY}}
Mobile app using openCV to wake up users that are dozing off when driving/working.
\sectionsep

% \runsubsection{CoderAIcing}
% \descript{| Web Developer}
% \location{February 2014 | HS Hacks I | \href{shantulshi.github.io}{shantulshi.github.io}}
% Educational app teaching users to write racings AIs used to compete with other users.
% \sectionsep

\runsubsection{Waffle}
\descript{| Android Developer}
\location{December 2013 | Angel Hacks | \href{https://sleepy-sands-6336.herokuapp.com/}{sleepy-sands-6336.herokuapp.com}}
Location based image sharing app that lets users post \& view images anonymously.
\end{minipage}
\end{document}
\documentclass[]{article}